---
title: " The report of the yelp project"
date: "`r date()`"
author: Frank(zhangc518@gmail.com)
output: 
    html_document:
      theme: united
      toc: true
      toc_depth: 2
      number_sections: true
      highlight: textmate
      fig_caption: yes 
      fig_width: 5
      fig_height: 4
      css: style.css
---
```{r,echo=F}
#install.packages(
#  'printr',
#  type = 'source',
#  repos = c('http://yihui.name/xran', 'http://cran.rstudio.com')
#)
library(printr)
```


# Introduction 

* [See task discription](Brainstroming.html)
* My question: What factor (location, parking, wifi, business hour, price and etc. ) contribute the most to the business’s review number and score

# Method and Data 

* Because my question is focused on business, so I will only use the business data. 

## The Raw data 

* File format: Json file 

List of the files: 

```{r,collapse=TRUE,cache=TRUE}
folder.main <- '~/Dropbox/coursera/Bigdata_tracker/10_capstone_1015/'
folder.data <- paste(folder.main,'data/',sep = "")
files.names <- dir(folder.data)
data.files <-grep(".json",files.names,value = T)
line.numbers<-sapply(data.files, function(x)
  system(paste("wc -l < ",paste(folder.data,x,sep="")),intern = T))
as.data.frame(line.numbers)
```

Business data:
```{r,cache=T}
library(rjson)
library(stringr)

# check if the business attributes consistent 
business.file <- grep("business",data.files,value = T)
business.clean <- data.frame(lon = rep(0,business.no),
                             lat = rep(0,business.no),
                             stars=rep(0,business.no),
                             review_count = rep(0,business.no))

con <- file(paste(folder.data,business.file,sep = ""),"r")
for(i in 1:business.no){
  print(i)
  tmp1<-fromJSON(readLines(con, 1));tmp1$categories;tmp1$name
  str(tmp1)
  business.clean[i,] <- c(tmp1$longitude,tmp1$latitude,tmp1$stars,tmp1$review_count)
}
close(con)
save.image(file="business.RData")



hist(business.clean$stars,breaks = seq(0,5,by=.5))
plot(business.clean$review_count,business.clean$stars)
image(x = as.matrix(business.clean[,1:3]))

tmp2<-fromJSON(business.line_1)
business.line_1 <- readLines(con, 1) ## Read the first line of text 
tmp3<-fromJSON(business.line_1)
close(con)

# build a clean data set (same as murder) 
business.wifi <-try(sapply(1:business.no, 
                           function(x) 
                           {print(x);fromJSON(readLines(con,1))}))

tmp1_1<- data.frame(lon=longitude,lat=tmp1$latitude,stars=tmp1$stars)
tmp1_1[2,] <- c(tmp2$longitude,tmp2$latitude,tmp2$stars)
tmp1_1
qmplot(lon,lat,data=tmp1_1,colour = I('red'), size = I(3), darken = .3)
head(murder)
head(tmp1_1)


# typical name structur 
str(tmp2)



### trying out ggmap package
install.packages("ggmap")
library(ggmap)

baylor <- "baylor university"
qmap(baylor, zoom = 14)
 geocode("the white house")
 qmap(baylor, zoom = 14, source = "osm")
 
set.seed(500)
df <- round(data.frame(
x = jitter(rep(-95.36, 50), amount = .3),
y = jitter(rep( 29.76, 50), amount = .3)
), digits = 2)
map <- get_googlemap('houston', markers = df, path = df, scale = 2)
ggmap(map, extent = 'device')

qmap(baylor, zoom = 14, source = "stamen", maptype = "watercolor") 
qmap(baylor, zoom = 14, source = "stamen", maptype = "toner")

 
map <- get_googlemap('houston', markers = df, path = df, scale = 2)
ggmap(map, extent = 'device')
?get_googlemap
map <- get_googlemap('usa', markers = business.clean[1:20,1:2],  scale = 2)


## show density 
load(file="./business.RData")
par(mfrow=c(1,1))
with(business.clean,smoothScatter(x = lon,y=lat))

#install.packages("rworldmap")
library(rworldmap)
newmap <- getMap(resolution = "low")
plot(newmap, xlim = c(-20, 59), ylim = c(35, 71), asp = 1)

with(business.clean,smoothScatter(x = lon,y=lat))
plot(newmap, xlim = c(-130,-60),
     ylim = c(20,60),asp=1)
with(business.clean,points(lon,lat,col="red",cex=.2,pch=16))
axis(1);axis(2);box()


### http://bcb.dfci.harvard.edu/~aedin/courses/R/CDC/maps.html
## ggmap for complex
library(ggmap)
#http://bcb.dfci.harvard.edu/~aedin/courses/R/CDC/maps.html
phoenixMap <- qmap('phoenix', zoom = 14,color = 'bw')
phoenixMap

phoenixBusiness <- subset(business.clean, -112.1 <= lon & lon <= 
    -112.05 & 33.43 <= lat & lat <= 33.47)
phoenixMap +geom_point(aes(x = lon, y = lat, 
  size = stars,colour = stars), data = phoenixBusiness )
range(phoenixBusiness$review_count)

# check review_count 
par(mfrow=c(1,2))
with(phoenixBusiness,plot(stars,review_count,main="phoenix"))
with(business.clean,plot(stars,review_count,main="all data"))
par(mfrow=c(1,1))
map <- get_map(location = 'phoenix az', zoom = 15,maptype = "roadmap")
?geom_point

ggmap(map) +geom_point(aes(x=lon,y=lat),data=business.clean,size=business.clean$stars/2,alpha=.5,colour=as.factor(business.clean$stars)) 
geocodeQueryCheck()


  
g + geom_point(aes(alpha=.001))

print(g)

d <- ggplot(diamonds, aes(carat, price)); 

d + geom_point(alpha = 1/10)
d + geom_point(alpha = 1/20)
d + geom_point(alpha = 1/100)


,alpha=0.01,size=sqrt(stars)),data=business.clean) 

?get_map


## map for simple map 
library(maps)
data(countyMapEnv)
head(countyMapEnv)
?map
map("state", interior = FALSE)
tmp<-map('county',region = c('arizona'))
map.text('county','arizona')
map.cities(us.cities,country = "AZ",label = T,cex=.5,capitals = 2)
map.axes()
with(business.clean,points(lon,lat,col="red",cex=.1,pch=1))

map("world", "China")
map.cities(country = "China", capitals = 2,label = T)



qplot(lon,lat,data=business.clean,colour=as.factor(stars))
range(business.clean$lon)
range(business.clean$lat)


#business.wifi <-try(sapply(1:business.no, 
#                           function(x) 
#                           {print(x);fromJSON(readLines(con,1))$attributes$`Wi-Fi`}))
#close(con)
#business.wifi_clean <- unlist(business.wifi)
#business.wifi_summary <-summary(factor(business.wifi_clean))
#business.wifi_summary["free"]/sum(business.wifi_summary)*100

```


## The data clean process 

```{r}

```


### About the Bussinesses 

For all the businesses in the data set, what is:

* total number 
* types:  

For each business, we can define attributes

* location: 
    + States 
    + City
    + longitude & latitude 
    + neighborhoods 
* **stars**
* review count



## 



```{r}
setwd('~/Documents/GitHub_Frank/yelp_project/') 
load(file="./qz1.RData")

```


# Results 

# Discussion 