---
title: " The report of the yelp project"
date: "`r date()`"
author: Frank(zhangc518@gmail.com)
output: 
    html_document:
      theme: united
      toc: true
      toc_depth: 2
      number_sections: true
      highlight: textmate
      fig_caption: yes 
      fig_width: 5
      fig_height: 4
      css: style.css
---
```{r,echo=F}
#install.packages(
#  'printr',
#  type = 'source',
#  repos = c('http://yihui.name/xran', 'http://cran.rstudio.com')
#)
library(printr)
```


# Introduction 

* [See task discription](Brainstroming.html)
* My question: What factor (location, parking, wifi, business hour, price and etc. ) contribute the most to the business’s review number and score

# Method and Data 

* Because my question is focused on business, so I will only use the business data. 

## The Raw data 

* File format: Json file 

List of the files: 

```{r,collapse=TRUE,cache=TRUE}
folder.main <- '~/Dropbox/coursera/Bigdata_tracker/10_capstone_1015/'
folder.data <- paste(folder.main,'data/',sep = "")
files.names <- dir(folder.data)
data.files <-grep(".json",files.names,value = T)
line.numbers<-sapply(data.files, function(x)
  system(paste("wc -l < ",paste(folder.data,x,sep="")),intern = T))
as.data.frame(line.numbers)
```

Business data:
```{r,cache=T}
library(rjson)
library(stringr)

## business
#business.no <-as.numeric(str_match(
#  string = grep("business",line.numbers,value = T)[[1]],pattern = "[0-9]+"))

business.file <- grep("business",data.files,value = T)
con <- file(paste(folder.data,business.file,sep = ""),"r")
business.line_1 <- readLines(con, 1) ## Read the first line of text 
tmp<-fromJSON(business.line_1)
business.line_1 <- readLines(con, 1) ## Read the first line of text 
tmp2<-fromJSON(business.line_1)
names(tmp2)
business.line_1
close(con)

#con <- file(paste(folder.data,business.file,sep = ""),"r")
#business.wifi <-try(sapply(1:business.no, 
#                           function(x) 
#                           {print(x);fromJSON(readLines(con,1))$attributes$`Wi-Fi`}))
#close(con)
#business.wifi_clean <- unlist(business.wifi)
#business.wifi_summary <-summary(factor(business.wifi_clean))
#business.wifi_summary["free"]/sum(business.wifi_summary)*100

```


## The data clean process 

```{r}

```


### About the Bussinesses 

For all the businesses in the data set, what is:

* total number 
* types:  

For each business, we can define attributes

* location: 
    + States 
    + City
    + longitude & latitude 
    + neighborhoods 
* **stars**
* review count



## 



```{r}
setwd('~/Documents/GitHub_Frank/yelp_project/') 
load(file="./qz1.RData")

```


# Results 

# Discussion 